A Large-Scale Study of the Use of Eval in R

### 2020-08-22 inst/paper/main.tex
intro

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above consider that R uses lazy evaluation like Haskell. The authors
  have informally surveyed end-users, some of them computer scientists, and
  did not find a single one aware of that fact. Library developers, on the
  other hand, tend to know about laziness and program defensively around
  it.}  Thus, our corpus distinguished between \emph{core packages} (there
are \miss{8} such packages that are loaded together with the R virtual
machine), \emph{CRAN packages} (these are curated packages that pass
stringent community quality checks and are equipped with tests and sample
data), \emph{scripts} (end-user written code that performs a particular
machine learning or data analysis task).

There are reasons to believe that usage patterns may be different. The core
R code is extremely stable, it has only been maintained for the last 20
years with very few far reaching changes. The libraries represent a more
lively ecosystem with new libraries added each day. Typically they are
developped by experience R developer.  Finally, end user code is often
written by non-programmers, data scientists who may or may not understand R.

To set up our experiements we have created a corpus composed of three
distinct data sets.  We have set out the 8 packages that are included with
the R virtual machine and refer to these as `` base'' packages.  We have
selected the 400 most widely included libraries and obtained a number of
client programs to exercises them.  Finally we have obtained 400 end users
programs from the Kaggle competition.

>>>>

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above consider that R uses lazy evaluation like Haskell. The authors
  have informally surveyed end-users, some of them computer scientists, and
  did not find a single one aware of that fact. Library developers, on the
  other hand, tend to know about laziness and program defensively around
  it.}  Thus, our corpus distinguished between \emph{core packages} (there
are \miss{8} such packages that are loaded together with the R virtual
machine), \emph{CRAN packages} (we selected \miss{500} curated packages that
pass stringent community quality checks and are equipped with tests and
sample data), \emph{scripts} (we used \miss{400} end-user written programs
that performs a particular data analysis task).  There are reasons to
believe that \eval usage patterns may differ between these datasets. The
core R code is extremely stable, it has only been maintained for the last 20
years with very few far reaching changes. The libraries represent a more
lively ecosystem with new libraries added each day.  Finally, end user code
is often one-use scripts thrown together and sometimes never revisited.
